---
title: "Tlajinga data cleaning"
author: "Maria C. Codlin"
date: "September 20, 2017"
output: html_document
---
In this document I will record my process of cleaning the data from my Tlajinga dataset for analysis. 
First I load the packages required
```{r load packages}
require(tidyr)
require(dplyr)
require(ggplot2)
```
And then the data set and call it PATT
```{r read data}
PATT<-tbl_df(read.csv("PATT_2017_V5_For_R.csv"))
Lote<-tbl_df(read.csv("PATT_Lote_R.csv"))
head(PATT)
head(Lote)
```
From Lote, I remove extra columns I had created which I no longer need and overwrite the df Lote.
```{r Clean Lote details}
Lote<-select(Lote, -X, -X.1, -X.2)
```
Since I have all the details about Lote stored in Lote, I can remove these details from my PATT database. I will keep them stored seperately however for now, just in case I encounter a discrepancy between the Lote df and the Lotes I analysed. 
```{r remove lote details from PATT}
PATT_Lote <-select (PATT, Lote:Fecha, Volume)
PATT<-select(PATT, -Volume, -(Operacion:Fecha))
head(PATT)
```

Now I want to attempt to summarise all of the Lote I analysed by linking the two tables. I think I need to rename the Operacion due to special characters. 
```{r Analysed Lote}
Lote_gr <-group_by(Lote, Unidad)
PATT_gr<-group_by(PATT, Lote)

analysed_Lotes <- inner_join(PATT_gr, Lote_gr, Lote)%>%
  Select(Lote, Operación, Unidad)%>%
  Unique%>%
  Print



```
```{r }

```



```{r }

```



```{r }

```



```{r }

```



```{r }

```



```{r }

```




```{r }

```